%-------------------------
% Resume in Latex
% Author : Srinivas Rao Tammireddy
% Based off of: https://github.com/srinu2003/LaTex-Resume
% License : MIT
%------------------------

% \documentclass[letterpaper,11pt]{article}
\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{bold-extra}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
% \addtolength{\oddsidemargin}{-0.5in}
% \addtolength{\evensidemargin}{-0.5in}
% \addtolength{\textwidth}{1in}
% \addtolength{\topmargin}{-.5in}
% \addtolength{\textheight}{1.0in}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\footskip}{4.08003pt}
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  %For bold small caps in Subheadings
  % \vspace{-4pt}\scshape\raggedright\large\bfseries 
  % For normal small caps in Subheadings
  \vspace{-6pt}\scshape\raggedright\large 
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% \usepackage{bold-extra} % for bold small caps in section titles and subheadings. Instead of \normalshape, use \scshape in:
% \textbf{\Huge \normalshape Srinivas Rao Tammireddy} \\ \vspace{1pt}


%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
\begin{center}
    {\Huge \scshape Srinivas Rao Tammireddy} \\ \vspace{2pt}
    Chintal, Hyderabad, Telangana 500054 \\ \vspace{1pt}
    \small \raisebox{-0.1\height}
    \faPhone\ +91 918-272-1417 ~
    \href{mailto:tsrin2003@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  {tsrin2003@gmail.com}} ~
    \href{https://linkedin.com/in/srinu2003/}{\raisebox{-0.2\height}\faLinkedin\ {linkedin.com/in/srinu2003}}  ~
    \href{https://github.com/srinu2003}{\raisebox{-0.2\height}\faGithub\ {github.com/srinu2003}}
    % \vspace{-8pt}
    % \vspace{16pt}
  \end{center}

%-----------OBJECTIVE-----------
\section{Objective}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \item \fontsize{10}{12} \selectfont
    A motivated Computer Science student with hands-on experience in software development, looking to leverage programming and problem-solving skills as an intern at Google.
  \end{itemize}
    


%-----------EDUCATION-----------
\vspace{-15pt}
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://mlritm.ac.in}{Marri Laxman Reddy Institute of Technology and Management}}{Nov. 2021 -- Present}
      {B.Tech - Computer Science and Engineering, 9.05/10 CGPA}{Hyderabad, IND}
    \resumeSubheading
      {Sri Chaitanya Junior College}{June 2019 -- Apr. 2021}
      {Science with Maths, 94.8\% Higher Secondary, JEE (Main) 2021 - 81.70 percentile}{Hyderabad, IND}
  \resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-3pt, parsep=3pt]
              \small
                \item Data Structures
                \item Database Management
                \item Algorithms Analysis
                \item Computer Architecture
                \item Operating Systems
                \item Software Engineering
                \item Computer Networks
                \item Cryptography
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}

    
%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://g.dev/tsrinu2003}{Programming Lead}}{June 2020 -- Present}
      {Google Developers Students Club}{MLRITM, Dundigal}
      \resumeItemListStart
        % \resumeItem{Led the development of a junior programming curriculum focused on Dart, including Bit Manipulation and Stacks/Queues data structures. Authored engaging competitive programming questions to challenge and develop problem-solving skills in junior members.}
        \resumeItem{Mentored juniors, improving their Technical relationship with Google Developer Tools.}
        \resumeItem{Organized workshops and bootcamps, fostering a collaborative learning environment.}
      \resumeItemListEnd
      

    \resumeSubheading
    {\href{https://drive.google.com/file/d/1Hg6w58KnwbqaRiJdtpxpFh-dshw1vEoR/view?usp=sharing}{UI/UX Hackathon}}{Sep. 2021}
    {MLRITM Department of C.S.E}{MLRITM, Dundigal}
      \resumeItemListStart
        \resumeItem{Designing adaptive UI/UX for cross-platform applications by Material-Design Design System.}
    \resumeItemListEnd

    \resumeSubheading{Kavach 2023}{Apr. 2023}{Inovation \& Incubation Center}{MLRITM, Dundigal}
      \resumeItemListStart
          \resumeItem{Participated in a 24-hour hackathon to develop a solution for a real-world problem.}
      \resumeItemListEnd
    \resumeSubheading{\href{http://kitsltd.co.uk/index.html}{Intern at KITS Ltd}}{June.2024}{Keertana Information Technology Solutions Limited}{KITS Ltd, UK}
        \resumeItemListStart
            \resumeItem{Developing an AI based Web portal using .NET}
        \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\href{https://github.com/srinu2003/Magpie}{{\textbf{Magpie}} $|$ \emph{Python, Tkinter}}}{Feb 12, 2024 -- May 15, 2024}
          \resumeItemListStart \vspace{0pt}
          \resumeItem{Developed a Python application using the Tkinter library for Encrypting \& Decrypting files.}
          \resumeItem{Implemented a command line interface (CLI) and implemented symmetric encryption (SHA-256) and hashing techniques using cryptography.fernet library.}
          \resumeItemListEnd
      \resumeProjectHeading
        {\href{https://github.com/srinu2003/quote_of_the_day}{{\textbf{Quotes of the Day}} $|$ \emph{Flutter, Dart, Firebase}}}{April 29, 2024 -- Present}
        \resumeItemListStart
          \resumeItem{Developing a mobile application that shows quote of the day.}
          \resumeItem{Implementing Firebase for user authentication and data storage and following Material-3 Design for UI/UX.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C Language, Dart, SQL (MySQL), HTML/CSS} \\
     \textbf{Developer Tools}{: Git, Github, Figma, Project IDX, Visual Studio Code, PyCharm, Star UML, Google Workspace, MS Excel, MS Word.} \\
     \textbf{Technologies/Frameworks}{: Unix/Linux, Flutter, Material-3 Design, App Script, \LaTeX, Version Control System} \\
    }}
 \end{itemize}

%-----------CODING PROFILES-----------
\vspace{-12pt}
\section{Coding Profiles}
\begin{multicols}{2}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \href{https://leetcode.com/tsrin2003/}{\underline{\textbf{Leetcode}}{:} @tsrin2003} 1,448 (Max Rating) \\
      \href{https://www.hackerrank.com/tsrin2003}{\underline{\textbf{HackerRank}}{:} @tsrin2003} C-Programming \\
      \href{https://www.interviewbit.com/profile/srinu2003/}{\underline{\textbf{InterviewBit}}{:} @srinu2003} 130638 (Global Rank) \\
      \href{https://www.codechef.com/users/srinu2003}{\underline{\textbf{CodeChef}}{:} @srinu2003} 1,641 (Max Rating) [3 Star] \\
      \href{https://codeforces.com/profile/srinu2003}{\underline{\textbf{Codeforces}}{:} @srinu2003} 858 (max. newbie, 858) \\
      }
    }
  \end{itemize}
\end{multicols}

%-----------CERTIFICATIONS/COURSES-----------
\vspace{-3pt}
  \section{Certifications/Courses}
    \resumeItemListStart[parsep = 0pt]
      \resumeItem{\href{https://drive.google.com/file/d/1pywMAJxX-Mg6qSX5HHIW5wEbV3PR07LQ/view?usp=drive_link}
                        {\textbf{Cisco Network Academy certification} -- Cyber Security \faExternalLink*} (Jul. 2022)}
      \resumeItem{\href{https://drive.google.com/file/d/1w72XSRwblf5AqqEBGvnUbvUayJTcpWO-/view?usp=drive_link}
                        {\textbf{Cisco Network Academy certification} -- Essential and Advanced C \faExternalLink*} (Aug. 2022)}
      \resumeItem{\href{https://www.udemy.com/certificate/UC-79138624-8361-423b-b131-42765a08db12/}
                        {\textbf{Python: The Professional Guide For Beginners (2024 Edition)} -- \href{https://www.linkedin.com/in/federicoazzu/}{Federico Azzurro} \faExternalLink*} (May. 2024)}
      \resumeItem{\href{https://www.hackerrank.com/certificates/607a2d4d88f1}
                        {\textbf{Python (Basic) certification} -- HackerRank \faExternalLink*} (May. 2024)}
    \resumeItemListEnd

  
%-----------INVOLVEMENT---------------
\vspace{-11pt}
\section{Honors and Awards}
  \resumeItemListStart[parsep = -2pt]
    \resumeItem{\textbf{Top 1} in Internal Coding Contest(Data Structures and Algorithms) conducted by Smart-Interviews, MLRITM}
    \resumeItem{Been class representative for 2 years in a row.}
  \resumeItemListEnd

%-------------------------------------------
\end{document}
